Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-02-27 paper.tex
correcciones menores de ortografia

Fig.~\ref{venn_2parameters} represents the situation when $\mathcal{K}_c$ is 
absent. Notice that $A/v_d$ or $k_t B$ may control the collective 
dynamic, in spite of the ``assertive'' attitude. The individual character of 
$v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
``loosely'' that any numerical \textcolor{blue}{\sout{setting} set for} these parameters may be 
counterbalanced by the right \textcolor{blue}{\sout{setting} choise } of $A$ or $k_t$, keeping the 
colletive dynamic (qualitatively) unchanged.  \\

@@

\item[(b)] We will consider the parameter \textcolor{blue}{set from} Ref.~\cite{helbing_2000} 
as a starting point for exploring the parameter space. The reason for this is 
that a complete set of experimental parameters is still not available (to our 
konwledge). We are aware, though, of the drawbacks \textcolor{blue}{for} this choise, say, the 
unrealistic meanings for the length $B$ and the compressibility $k_n$ (see 
Section~\ref{experimental}). But these are irrelevant in the context of the 
(\textcolor{blue}{dimensionless}) parameter space and the corresponding collective dynamics (see 
Section~\ref{introduction}).

@@

The implemented SFM parameters were the same as those in 
Ref.~\cite{helbing_2000} (at the beginning of the exploratory procedure only). 
But the pedestrian's mass and radius were set to the more realistic values of 
$70\,$kg and $0.23\,$m, respectively. The force interactions between 
pedestrians were limited, however, to a cut-off distance of $0.88\,$m for 
attaining a \textit{privacy sphere} \textcolor{blue}{for the first neighbors only}. The desired 
velcity was always set to $1\,$m/s in the corridor situation. Besides, the 
explored values of $v_d$ for the bottleneck scenario ranged from $1\,$m/s to the 
extremely anxious situation of $10\,$m/s. \\

@@

We can test our hypothesis by computing the mean overlap. 
Fig.~\ref{overlap_dens} shows this magnitude for the corridor situation. Notice 
that ``soft'' pedestrians attain \textcolor{blue}{\sout{a more intruding} more } overlap than the ``stiff'' 
ones, as expected. This is in agreement with Fig.~\ref{overlap_vd} for the 
bottleneck situation (at a fixed value of $v_d$). The curves in 
Fig.~\ref{overlap_vd}, however, do not meet each other as in  
Fig.~\ref{overlap_dens}. \textcolor{red}{\sout{The curve meeting attains for space limitations in 
the corridor, since overlapping occurs (almost) independently of the value of
$k_n$. This is clearly not the case in the bottleneck situation.} 
All the curves meet each other at high-density values. This phenomenon occurs
due to space limitations in the corridor that produces overlapping (almost) independently of the
value of k n}. \\

@@

The above results correspond to \textcolor{blue}{\sout{a milestone} an important step} in the 
investigation. The \textcolor{blue}{inter-pedestrian} connectivity differences between the bottleneck geometry 
and the corridor geometry were not expected and opens two major questions:
\textcolor{blue}{\sout{ how 
does the body stiffness interact with the walls} how do the pedestrians interact with the walls as
a function of the body stiffness}, and consequently, how does 
this affect the flux across the corridor.\\

>>>>

Fig.~\ref{venn_2parameters} represents the situation when $\mathcal{K}_c$ is 
absent. Notice that $A/v_d$ or $k_t B$ may control the collective 
dynamic, in spite of the ``assertive'' attitude. The individual character of 
$v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
``loosely'' that any numerical \textcolor{blue}{\sout{setting} set for} these parameters may be 
counterbalanced by the right \textcolor{blue}{\sout{setting} choice } of $A$ or $k_t$, keeping the 
colletive dynamic (qualitatively) unchanged.  \\

@@

\item[(b)] We will consider the parameter \textcolor{blue}{set from} Ref.~\cite{helbing_2000} 
as a starting point for exploring the parameter space. The reason for this is 
that a complete set of experimental parameters is still not available (to our 
konwledge). We are aware, though, of the drawbacks \textcolor{blue}{of} this choice, say, the 
unrealistic meanings for the length $B$ and the compressibility $k_n$ (see 
Section~\ref{experimental}). But these are irrelevant in the context of the 
(\textcolor{blue}{dimensionless}) parameter space and the corresponding collective dynamics (see 
Section~\ref{introduction}).

@@

The implemented SFM parameters were the same as those in 
Ref.~\cite{helbing_2000} (at the beginning of the exploratory procedure only). 
But the pedestrian's mass and radius were set to the more realistic values of 
$70\,$kg and $0.23\,$m, respectively. The force interactions between 
pedestrians were limited, however, to a cut-off distance of $0.88\,$m for 
attaining a \textit{privacy sphere} \textcolor{blue}{that excludes second neighbors}. The desired 
velcity was always set to $1\,$m/s in the corridor situation. Besides, the 
explored values of $v_d$ for the bottleneck scenario ranged from $1\,$m/s to the 
extremely anxious situation of $10\,$m/s. \\

@@

We can test our hypothesis by computing the mean overlap. 
Fig.~\ref{overlap_dens} shows this magnitude for the corridor situation. Notice 
that ``soft'' pedestrians attain \textcolor{blue}{\sout{a more intruding} more } overlap than the ``stiff'' 
ones, as expected. This is in agreement with Fig.~\ref{overlap_vd} for the 
bottleneck situation (at a fixed value of $v_d$). The curves in 
Fig.~\ref{overlap_vd}, however, do not meet each other as in  
Fig.~\ref{overlap_dens}. \textcolor{red}{\sout{The curve meeting attains for space limitations in 
the corridor, since overlapping occurs (almost) independently of the value of
$k_n$. This is clearly not the case in the bottleneck situation.} 
All the curves meet each other at high-density values. This phenomenon occurs
due to space limitations in the corridor that produces overlapping (almost) independently of the
value of $k_n$}. \\

@@

The above results \textcolor{blue}{\sout{correspond to a milestone} represent an important step} in the 
investigation. The \textcolor{blue}{inter-pedestrian} connectivity differences between the bottleneck geometry 
and the corridor geometry were not expected and opens two major questions:
\textcolor{blue}{\sout{ how 
does the body stiffness interact with the walls} how do the pedestrians interact with the walls as
a function of the body stiffness}, and consequently, how does 
this affect the flux across the corridor.\\
